---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# sql.helper

The goal of sql.helper is to help building SQL queries in R


## Install

```
# install.packages('devtools')
devtools::install_github("taekyunk/sql.helper")
```

## Example: `paren()`

This is a basic example of using `paren()` with SQL IN operator.

```{r example}
id_char <- as.character(1:5)
id_num <- 3:8

# paren() will add single quotes if the field is not numeric
paren(id_char)
paren(id_num)

# to match character with numeric
paren(as.numeric(id_char))

# to match numeric with character
paren(as.character(id_num))

# typical use case will be something like this
query <- paste("select * from tablename where id in", paren(id_num), ";")
print(query)
```


## Example: `count_from()`

`count_from()` can be used to build SQL query to count the combination of variables.

```{r example2}
library(tidyverse)
c("x", "y") %>% 
    count_from("schema.table")
```

## Example: `count_rows()`

`count_rows()` builds SQL query to count the number of observations in a table

```{r example3}
count_rows("schema.table")
```

## Example: `add_limit()`

`add_limit(n)` adds limit condition at the end of the given SQL query

```{r example4}
"select * from schema.table;" %>% add_limit(100)
```
